Generic Cormotif

### 2017-11-21 paper/main.tex
update paper
paper

\section{Introduction}
%\textit{lfdr}
\section{Methods}

@@

By Bayes theorem, 
\begin{eqnarray}
&&p(\beta_{jr}|\hat\beta,\hat s,\pi, g) = p(\beta_{jr}|\hat\beta_{j},\hat s_j,\pi, g)\nonumber \\
&=& \sum_{k=1}^Kp(\beta_{jr}|\hat\beta_{j},\hat s_j,\pi,g,z_j=k)p(z_j=k|\hat\beta_{j},\hat s_j,\pi, g) \nonumber\\
&=& \sum_{k=1}^Kp(\beta_{jr}|\hat\beta_{jr},\hat s_j,\pi,g,z_j=k)p_{jk}\nonumber \\
&=& \sum_{k=1}^K\frac{p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})g_{kr}(\beta_{jr})}{\int p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})g_{kr}(\beta_{jr})d\beta_{jr}}\times p_{jk} \nonumber\\
&=& \sum_{k=1}^K \frac{\sum_{l=0}^Lw_l^{kr}\tilde f_{l}(\hat\beta_{jr})h_{l}(\beta_{jr}) }{\sum_{l'=0}^Lw_{l'}^{kr}\tilde f_{l'}(\hat\beta_{jr})} \times p_{jk} \nonumber\\
&=& \sum_{l=0}^L \theta_{ljr}h_{l}(\beta_{jr}). 
\end{eqnarray}
Here the posterior mixture component $h_l$ is the posterior on $\beta_{jr}$ that would be obtained using prior $f_l(\beta_{jr})$ and likelihood $p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})$, and the mixture weights $\theta_{ljr}$ is
\begin{equation}
     \theta_{ljr} = \sum_{k=1}^K\frac{w_{l}^{kr}\tilde f_{l}(\hat\beta_{jr})p_{jk}}{\sum_{l'=0}^L\eta_{l'r}\tilde f_{l'jr}(\hat\beta_{jr})}.
\end{equation}

% where $f_0$ is a point mass on 0. Then we have 
% \begin{equation}
%     p(\beta_{jr}|\pi,g,\hat s) = \sum_{k=1}^K\pi_k g_{kr}(\beta_{jr})=  \sum_{k=1}^K\pi_k\sum_{l=0}^Lw_l^{kr}f_l(\beta_{jr})
%     = \sum_{l=0}^L\eta_{lr}f_l(\beta_{jr}),
% \end{equation}
% where $\eta_{lr}=\sum_{k=1}^K\pi_kw_l^{kr}$. Thus, by (\ref{eq:5}), we get
% \begin{equation}
%     p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr},\pi, g) = \sum_{l=0}^L\theta_{ljr}p_{l}(\beta_{jr}|\hat\beta_{jr},\hat s_{jr}).
% \end{equation}
% The posterior mixture component $p_l$ is the posterior on $\beta_{jr}$ that would be obtained using prior $f_l(\beta_{jr})$ and likelihood $p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})$. To compute the mixture weights $\theta_{ljr}$, denote
% \begin{equation}
%     \tilde f_{ljr}(\hat\beta_{jr}) := \int f_l(\beta_{jr})p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})d\beta_{jr},
% \end{equation}
% the convolution of $f_l$ and a density function. Then $\theta_{ljr}$ can be obtained from
% \begin{equation}
%     \theta_{ljr} = \frac{\eta_{lr}\tilde f_{ljr}(\hat\beta_{jr})}{\sum_{l'=0}^L\eta_{l'r}\tilde f_{l'jr}(\hat\beta_{jr})}.
% \end{equation}

>>>>

\section{Introduction}

We introduce a new Empirical Bayes approach for jointly analyzing differential gene expression in multiple studies or under multiple experimental conditions (e.g., measured in different cell types), which allows for correlations among studies. Compared with existing methods, the new approach improves power and effect-size estimation. Model fitting procedures are implemented using expectation maximization (EM).
%\textit{lfdr}
\section{Methods}

@@

By Bayes theorem, 
\begin{eqnarray}
&&p(\beta_{jr}|\hat\beta,\hat s,\pi, g) = p(\beta_{jr}|\hat\beta_{j},\hat s_j,\pi, g)\nonumber \\
&=& \sum_{k=1}^Kp(\beta_{jr}|\hat\beta_{j},\hat s_j,\pi,g,z_j=k)p(z_j=k|\hat\beta_{j},\hat s_j,\pi, g) \nonumber\\
&=& \sum_{k=1}^Kp(\beta_{jr}|\hat\beta_{jr},\hat s_j,\pi,g,z_j=k)p_{jk}\nonumber \\
&=& \sum_{k=1}^K\frac{p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})g_{kr}(\beta_{jr})}{\int p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})g_{kr}(\beta_{jr})d\beta_{jr}}\times p_{jk} \nonumber\\
&=& \sum_{k=1}^K \frac{\sum_{l=0}^Lw_l^{kr}\tilde f_{l}(\hat\beta_{jr})h_{l}(\beta_{jr}) }{\sum_{l'=0}^Lw_{l'}^{kr}\tilde f_{l'}(\hat\beta_{jr})} \times p_{jk} \nonumber\\
&=& \sum_{l=0}^L \theta_{ljr}h_{l}(\beta_{jr}). 
\end{eqnarray}
Here the posterior mixture component $h_l$ is the posterior on $\beta_{jr}$ that would be obtained using prior $f_l(\beta_{jr})$ and likelihood $p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})$, and the mixture weights $\theta_{ljr}$ is
\begin{equation}
     \theta_{ljr} = \sum_{k=1}^K\frac{w_{l}^{kr}\tilde f_{l}(\hat\beta_{jr})p_{jk}}{\sum_{l'=0}^L\eta_{l'r}\tilde f_{l'}(\hat\beta_{jr})}.
\end{equation}

% where $f_0$ is a point mass on 0. Then we have 
% \begin{equation}
%     p(\beta_{jr}|\pi,g,\hat s) = \sum_{k=1}^K\pi_k g_{kr}(\beta_{jr})=  \sum_{k=1}^K\pi_k\sum_{l=0}^Lw_l^{kr}f_l(\beta_{jr})
%     = \sum_{l=0}^L\eta_{lr}f_l(\beta_{jr}),
% \end{equation}
% where $\eta_{lr}=\sum_{k=1}^K\pi_kw_l^{kr}$. Thus, by (\ref{eq:5}), we get
% \begin{equation}
%     p(\beta_{jr}|\hat\beta_{jr},\hat s_{jr},\pi, g) = \sum_{l=0}^L\theta_{ljr}p_{l}(\beta_{jr}|\hat\beta_{jr},\hat s_{jr}).
% \end{equation}
% The posterior mixture component $p_l$ is the posterior on $\beta_{jr}$ that would be obtained using prior $f_l(\beta_{jr})$ and likelihood $p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})$. To compute the mixture weights $\theta_{ljr}$, denote
% \begin{equation}
%     \tilde f_{ljr}(\hat\beta_{jr}) := \int f_l(\beta_{jr})p(\hat\beta_{jr}|\beta_{jr},\hat s_{jr})d\beta_{jr},
% \end{equation}
% the convolution of $f_l$ and a density function. Then $\theta_{ljr}$ can be obtained from
% \begin{equation}
%     \theta_{ljr} = \frac{\eta_{lr}\tilde f_{ljr}(\hat\beta_{jr})}{\sum_{l'=0}^L\eta_{l'r}\tilde f_{l'} (\hat\beta_{jr})}.
% \end{equation}
